Topic Modeling of News

### 2017-10-23 paper/R/webhoseio_explore.Rmd
new

df %>% filter(site != "zdf.de") -> df
col <- brewer.pal(12, name = "Paired")
```

## Count number of terms in a string
```{r}
df$text_lenght <- sapply(gregexpr("\\S+", df$text), length)
```

@@

```{r}
save(df, file="../output/news_cleaned.Rda")
```

```{r}
df$btw <- ifelse(grepl("Bundestagswahl", df$text, ignore.case = TRUE), 1,0)
```

### Number of published Articels by News Source

```{r}
ggplot(df, aes(site)) +
  geom_bar(fill="blue", alpha = .5) +
  xlab("") +
  ylab("Number of Articles") +
  theme(axis.text.x = element_text(angle = 40, hjust = 1))
```

### Share of Articles mentioning Bundestagwahl
```{r}
df %>%
  group_by(site, btw) %>%
  tally() %>%
  group_by(site) %>%
  mutate(n_total = sum(n)) -> count

count %>%
  filter(btw == 1) %>%
  ggplot(aes(site, n/n_total)) +
  geom_col(fill="blue", alpha=.5) +
  xlab("") +
  ylab("Share of Articles mentioning Bundestagwahl") +
  theme(axis.text.x = element_text(angle = 40, hjust = 1))
```

```{r}
btw <- df[which(df$btw == 1),]
```

@@

## Remove Stopwords
```{r}
btw$text_cleaned<- removeWords(btw$text_cleaned, stopwords("german"))
```

@@

>>>>

col <- brewer.pal(12, name = "Paired")
```

@@

@@

## Remove Stopwords
```{r}
df$text_cleaned<- removeWords(df$text, stopwords("german"))
```

## Tokenize terms
```{r}
news_words <- df %>%
  unnest_tokens(word, text) %>%
  count(site, word, sort = TRUE)

@@

```.
